Are populations like a circuit? Comparing isolation by resistance to a new coalescent-based method.

### 2019-04-18 review-responses.tex

\begin{point}{}
    ``suppose that the spatial arrangement of populations is given by a graph
    \ldots''  ``Graph'' is a very general term and not clear exactly what is meant
    here.  If the word has a more specific meaning in this context, please
    define it.
\end{point}

\reply{
    Done. \revref
}

\begin{point}{Fig 6 caption:}
    the barrier is ``sufficiently thick'' to prohibit migration.  ``Thick''
    implies distance, but is that a requirement?  Couldn’t the barrier be
    higher or deeper or less penetrable for a different reason than thickness?
\end{point}

\reply{
    Yes, but this is the way we implemented it in the simulation.
}

@@

\begin{quote}
    This is a polished theoretical and methodological contribution towards
    understanding the genetic processes that affect genetic distance and thus
    connectivity of species across the landscape. The authors make a
    little-appreciated point about considering the coalescent time as a
    predictor of genetic distance as opposed to resistance distance which can
    result in spurious results  where genetic distance is shaped by
    asymmetrical gene flow and coalescent processes.

    There are some points of clarification however that I think need to be made
    so that the paper is accessible and clear to its intended audience, and to
    ensure the paper can be adopted and influence analyses in this area. The
    differences in the highly spatial resistance distance approach versus the
    genetics-based coalescent time-based approach need to be distinguished more
    clearly, as in some ways this may be seen as comparing apples and oranges.
    Issues around timescales of genetic change (effects of landscape vs
    coalescent times) need to be further addressed and elucidated.  The
    differences in the results gained from the approaches are clearly defined
    and presented however.

    The types of questions and the type of demographic scenarios under which
    resistance vs. coalescense based approaches may be an improvement, or
    combined in the same study should be made more clearly. I suggest a
    summarising table or flow chart to this effect, that addresses time scales
    also.
\end{quote}

We've added more discussion along these lines
particularly in {\llname{ll:history}} 
and in relation to analysis of the poplar data.
We've got quite a few figures already (and have added one for the poplars),
so haven't tried to add a flow chart.

\begin{point}{Line 7 of abstract and generally:}
    This statement is conditional on the characteristics of the data you have, and
    your study aim. If the study aim is to  ask how landscape features affect
    genetic distance, then the coalescent time is not going to explicitly test
    this, or? It needs to be made clear how different study objectives will
    benefit in landscape genetics and under what circumstances a `more
    accurate' predictor of genetic distance can be gained. It seems appropriate
    to mention that this approach would greatly complement existing landscape
    genetic analysis approaches to see the relative effects of resistance and
    coalescent time. Implications for management decisions based on resistance
    models could be mentioned, as resistance models are intended to inform
    conservation decisions in some cases.
\end{point}

\reply{
    We're not sure which possible study aims are being referred to,
    but one possible aim that is not possible currently with coalescence methods
    is to produce high-resolution maps (as we discuss, \revref).
    We made the statement that
    genetic data are more accurately modeled by coalescence time than resistance distance
    because while there is an extensive literature going back fourty years
    describing the broad conditions under which coalescence is a good model 
    for the process that produces genomic data,
    we know of no such justification for resistance distance.
    Perhaps the key disconnect here is that we're thinking about generative models?
    We agree that since coalescence theory does not always apply,
    resistance distance on some network could in principle be closer to the truth
    than any coalescence times.
    However, we're unaware of this claim having been made.
    Furthermore, as we understand it,
    the point of landscape genetics methods using resistance distance
    is not merely to recapitulate observed genetic distances,
    but to provide an accurate depiction of past or present gene flow,
    i.e., movements of individuals across the landscape,
    In our paper we've tried to describe how inaccuracies of the generative model
    that underlies resistance distance
    can lead to misleading results.
    As discussed at \llname{ll:approx},
    resistance distance is used only because it is a more computationally tractable
    approxmation to coalescence time --
    any method that uses resistance distances could in principle be 
    done with coalescence times instead (e.g., to look at the effect of landscape features).
    This is discussed at \llname{ll:circuitscape}.
}

\begin{point}{\revref}
    Extremely long sentence, please divide.
\end{point}

\reply{
    Done.
}

@@

\begin{point}{\revref}
    Would it make sense to select genetic markers that are more informative for
    coalescence rates by narrowing the level of variation accepted in the
    model? Would this help error rates justifiably or just bias interpretation?
\end{point}

\reply{
    This is an interesting idea,
    and suggests looking at a statistic of genetic differentiation other than the mean,
    perhaps IBD segment lengths (as done by \citet{alasadi2018estimating}).
    We don't know enough about this to speculate, however.
}
